Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-08-20 paper/suppl.tex
some (non-caption) text for surface plots

@@

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
Reliably across all five movie contrasts, we find bilaterally significant
clusters that overlap with the PPA group overlap
(see Figure~\ref{fig:stability-slices}).
% AV: RSC & LOC
Several contrasts of the movie also yielded bilaterally significant clusters in
the ventral precuneal cortex and posterior cingulate gyrus (i.e. retrosplenial
complex; contrasts 1, 4, 5), and lateral occipital cortex (contrasts 1, 2, 4,
5).

@@

\subsection*{Surface maps}

\todo[inline]{Just mention this part in the main document via 'the corresponding
surface plots (Fig xy) can be found in the supplemental materials'?}
\todo[inline]{write intro regarding purpose of additional surface plots?}

% reconstruction MNI
Cortical reconstruction of the MNI152 T1-weighted brain template
[MNI152\_T1\_1mmi\_brain.nii.gz] was performed using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
\citep{dale1999cortical}.
% reconstruction: individual results
Subject-specific cortical surfaces are part of pre-existing
\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
an additional high-resolution T2-weighted image.

% projection
Results were projected onto the corticals surface using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
'mri\_vol2surf' command.
% smoothing
Group and individual PPAs were additionally patially smoothed applying a
Gaussian kernel with full width at half maximum (FWHM) of \unit[3.0]{mm}.

\subsubsection*{Group results}
Group results see Table~\ref{tab:res-ao-group1} for AO results,
Table~\ref{tab:res-av-group1} for AV results, and
Figure~\ref{fig:grp_ao_av_c1_surf} for surface maps.

\subsubsection*{Stability}
Group results see Figure~\ref{fig:grp_ao_av_stability} for surface maps.

\subsubsection*{Individual results}

\todo[inline]{RSC in of AV is essentially not visible}

Individual results see Figure~\ref{fig:subjs_ao_av_c1_surf} for surface maps.

@@

\setcounter{figure}{0}

>>>>

\todo[inline]{Position der Abbildungen ist im kompilierten PDF maximal
verwirrend}

\subsubsection*{Surface plot of group results}

% intro
Figure~\ref{fig:grp_ao_av_c1_surf} shows the group results for/of/from the
movie's primary contrast (\texttt{vse\_new > vpe\_old}) and audio-description's
primary contrast (\texttt{geo, groom} > non-spatial noun categories) mapped onto
the cortical surface of the MNI152 T1-weighted brain template.
% mapping procedure
Cortical reconstruction of the MNI152 template was performed using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
\citep{dale1999cortical}.
% projection
Results were projected onto the corticals surface using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
'mri\_vol2surf' command.
% smoothing
The union of individual PPAs was spatially smoothed applying a Gaussian kernel
with full width at half maximum (FWHM) of \unit[3.0]{mm}.

\subsubsection*{Surface plot of individual results}

% intro
Figure~\ref{fig:subjs_ao_av_c1_surf} shows the individual results for/of/from
the movie's primary contrast (\texttt{vse\_new > vpe\_old}) and
audio-description's primary contrast (\texttt{geo, groom} > non-spatial noun
categories) mapped onto subject-specific cortical surfaces.
% source of surfaces
Individual surfaces were provided by a preexisting
\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
an additional high-resolution T2-weighted image.
% projection
Results were projected onto the cortical surfaces using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
'mri\_vol2surf' command.
% smoothing
Individual PPA ROIs were spatially smoothed applying a Gaussian kernel with full
width at half maximum (FWHM) of \unit[3.0]{mm}.

@@

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
Reliably across all five movie contrasts, we find bilaterally significant
clusters that overlap with the PPA group overlap (see
Figure~\ref{fig:stability-slices} and Figure~\ref{fig:grp_ao_av_stability}).
% AV: RSC & LOC
Several contrasts of the movie also yielded bilaterally significant clusters in
the ventral precuneal cortex and posterior cingulate gyrus (i.e. retrosplenial
complex; contrasts 1, 4, 5), and lateral occipital cortex (contrasts 1, 2, 4,
5).

@@

@@
